A Latex Coursework Example

### 2012-07-18 docs/dissertation/MSc-coursework.tex
dissertation template

\documentclass[12pt,a4paper]{report}

@@

% the following 4 lines are the content of the smallmargins.sty file
% but including them explicitly makes this more portable.
%AC%\oddsidemargin=0.1in
%AC%\topmargin=-0.5in
%AC%\textheight=9in
%AC%\textwidth=6.25in

%AC%\parskip 10pt
%AC%\parindent 0in

@@

%AC%\pagestyle{myheadings}
%AC%\markright{D.~S.~Henty}

%\title{A Latex thesis example}
%\author{D.~S.~Henty}
%\date{\today}

%\maketitle

\title{Live Benchmarking Scientific Application in HPC Cloud}
\author{Author's Name}
\date{\today}

@@

\vspace{12cm}

\begin{center}

\large{MSc in High Performance Computing}

\large{The University of Edinburgh}

\large{Year of Presentation: 2007}

\end{center}

@@

\begin{abstract}
This is the bit where you summarise what is in your thesis.
\end{abstract}

@@

\tableofcontents
\listoftables
\listoffigures

\begin{titlepage}
\vspace*{2in}
% an acknowledgements section is completely optional but if you decide
% not to include it you should still include an empty {titlepage}
% environment as this initialises things like section and page numbering.
\section*{Acknowledgements}

@@

\end{titlepage}

\pagenumbering{arabic}

\chapter{Introduction}
This should contain a description of your project and the problem you
are trying to solve. Where appropriate you should also include
references to work which has already been done on your topic and
anything else which lets you set your work in context.

@@

\chapter{Background theory}

\section{The easy bits}
This is just to show how to break things into sections.

@@

\section{The more difficult bits}
Some bits are hard.

@@

\subsection{Hard bits}
You might want to include an equation here:

@@

\subsection{Even harder bits}
This might be one of the places where you might want to refer to
equation \ref{equation:delsplit}. You will usually need to use the
Latex command twice to make cross-references like this work properly.
The cross-reference information is stored in the {\em .aux} file so don't
delete it.

\subsubsection{Numbering}
You can keep subdividing but eventually you get to a level where
numbering stops. This text is in a subsubsection which is not numbered
by default.

@@

This text is in a paragraph which is also not numbered by default and
the ``title'' of the paragraph is not on a separate line.
If you want to increase the depth to which sections are numbered you
should see the section on setting the secnumdepth counter in the manual.

\chapter{Experimental design}

@@

\begin{center}
\resizebox{0.30\hsize}{!}{\includegraphics{/usr/local/share/logos/eucrest}}
\end{center}

@@

\chapter{Results and Analysis}

\section{Some results}
Here are some results.

\subsection{More results}
When showing results you are likely to use tables and graphs. You can
create tables easily in Latex.

@@

One of the simplest ways to produce simple graphs is to use gnuplot
which produces Latex output. Graph \ref{fig:gnu} was produced using
gnuplot with output designated as Latex so that a Latex output file is
produced which you can include directly or keep separate and refer to
using the {\em include} command.

@@

Perhaps the most robust way to include graphs is to convert them to
PostScript or PDF and include them in the same was as was done in
Figure~\ref{fig:eucrest} for the University Crest. You can usually do
this with most packages, including Microsoft ones; one trick for
producing PostScript is to print to a dummy PostScript printer.

@@

\chapter{Conclusions}

This is the place to put your conclusions about your work. You can
split it into different sections if appropriate. You may want to include
a section of future work which could be carried out to continue your
research.

\appendix
% the appendix command just changes heading styles for appendices.

\chapter{Stuff which is too detailed}

Appendices should contain all the material which is considered too
detailed to be included in the main bod but which is, nevertheless,
important enough to be included in the thesis.

\chapter{Stuff which no-one will read}

Some people include in their thesis a lot of detail, particularly
computer code, which no-one will ever read. You should be careful that
anything like this you include should contain some element of uniqueness
which justifies its inclusion.

>>>>

\documentclass[12pt,a4paper]{article}

@@

@@

\title{A Latex Coursework Example}
\author{David Henty}
\date{\today}

@@

@@

@@

\tableofcontents

\section*{Acknowledgements}

@@

\section*{Note}

This template was originally created for a full MSc dissertation.
Although I have modified the format slightly (eg there are no separate
chapters), I have not substantially changed the text or the advice
appearing in the \LaTeX comments (source lines beginning with \%). You
should therefore be aware that for a short piece of coursework you may
not need to go into as much detail as indicated here. For example, you
might not need to include any acknowledgements and any reference list is
likely to be very short.

\newpage
\pagenumbering{arabic}

\section{Introduction}

This should contain a description of your project and the problem you
are trying to solve. Where appropriate you should also include
references to work which has already been done on your topic and
anything else which lets you set your work in context.

@@

\subsection{The easy bits}
This is just to show how to break things into sections.

@@

\subsection{The more difficult bits}
Some bits are hard.

@@

\subsubsection{Hard bits}
You might want to include an equation here:

@@

\subsubsection{Even harder bits}
This might be one of the places where you might want to refer to
equation \ref{equation:delsplit}. You will usually need to use the
Latex command twice to make cross-references like this work properly.
The cross-reference information is stored in the {\em .aux} file so don't
delete it.

@@

This text is in a paragraph which is also not numbered by default and
the ``title'' of the paragraph is not on a separate line.
If you want to increase the depth to which subsections are numbered you
should see the subsection on setting the secnumdepth counter in the manual.

\section{Experimental design}

@@

\begin{center}
\resizebox{0.30\hsize}{!}{\includegraphics{logos/eucrest}}
\end{center}

@@

\section{Results and Analysis}

\subsection{Some results}
Here are some results.

\subsubsection{More results}
When showing results you are likely to use tables and graphs. You can
create tables easily in Latex.

@@

One way to produce simple graphs is to use gnuplot which can produce
native Latex output. Graph \ref{fig:gnu} was produced using gnuplot with
output designated as Latex; this creates a Latex output file which you
can include directly or keep separate and refer to using the {\em
include} command.

@@

Perhaps the most robust way to include graphs is to create then using
whatever package you like (eg Excel) and then convert them to PostScript
or PDF and include them in the same was as was done in
Figure~\ref{fig:eucrest} for the University Crest. You can usually do
this with most packages, including Microsoft ones. One trick for
producing PostScript is to print to a dummy PostScript printer; for PDF
you can use the free CutePDF utilities at {\verb+www.cutepdf.com+}.

@@

\section{Conclusions}

This is the place to put your conclusions about your work. You can
split it into different subsections if appropriate. You may want to include
a subsection of future work which could be carried out to continue your
research.
